\ttitle

### 2015-06-02 Chapters/Introduction.tex
Testing bash

Pancreaticoduodenectomy was initially described as a two-stage procedure where the first stage involved a biliary bypass aimed at relieving obstructive jaundice before the second stage of resection was carried out.

>>>>

Pancreaticoduodenectomy -Whipple was initially described as a two-stage procedure where the first stage involved a biliary bypass aimed at relieving obstructive jaundice before the second stage of resection was carried out.
